---
title: "Analysis_of_Country"
output: html_document
date: "2023-03-13"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## No. of Billionaires by Country
```{r}
billionaires_country <- billionaires %>% 
  count(country) %>% 
  arrange(-n) %>% 
  head(10) %>% 
  ggplot(aes(x=reorder(country,n), y=n))+
  geom_col(color = "black", fill ="coral1")+
  coord_flip()+
  labs(title = "No. of Billionaires by Country",
       x = "Country",
       y = "Number of Billionaires")
```

```{r}
billionaires_country+
  theme_linedraw()+
  theme(plot.title = element_text(size = 10, face = "bold"),
        axis.title = element_text(size=10),
        axis.text.x = element_text(size=9, hjust=1))
```

## Companies by country Pie Chart
```{r}
companies %>% 
  count(country) %>% 
  arrange(-n) %>% 
  head(10) %>% 
  ggplot(aes(x=country, y=n, fill=country))+
  geom_col()+
  coord_polar()
```

## Comparison of highest market value to lowest market value

Highest market value - top 10
```{r}
companies_MV_high <- companies %>% 
  arrange(-market_value_bil) %>% 
  head(10) %>% 
  select(global_company, country, market_value_bil) %>% 
  ggplot(aes(x=reorder(global_company, market_value_bil), y=market_value_bil, fill = country))+
  geom_col(color = "black")+
  coord_flip()+
  labs(title = " Highest Market Values of the Top 10 Global Companies by Country",
       x = "Market Value",
       y = "Global Company")
```

```{r}
companies_MV_high+
  theme_linedraw()+
  theme(plot.title = element_text(size = 10, face = "bold"),
        axis.title = element_text(size=10),
        axis.text.x = element_text(size=9, hjust=1))
```

Lowest Market Value - Lower 10
```{r}
companies_MV_low <- companies %>% 
  arrange(market_value_bil) %>% 
  head(10) %>% 
  select(global_company, country, market_value_bil) %>% 
  ggplot(aes(x=reorder(global_company, market_value_bil), y=market_value_bil, fill = country))+
  geom_col(color = "black")+
  coord_flip()+
  labs(title = "Lowest Market Values of the Top 10 Global Companies by Country",
       x = "Market Value",
       y = "Global Company")
```

```{r}
companies_MV_low+
  theme_linedraw()+
  theme(plot.title = element_text(size = 10, face = "bold"),
        axis.title = element_text(size=10),
        axis.text.x = element_text(size=9, hjust=1))
```

Conclusion: the US is the best country to be in to maximise your chances of becoming a billionaire.

## Arranging Billionaires by final worth and seeing which states have the highest

```{r}
billionaires
```

```{r}
billionaires %>%
  select(rank, person_name, final_worth, state) %>%
  filter(state!="NA") %>%
  arrange(-final_worth) %>%
  count(state) %>%
  arrange(-n)
```

```{r}
billionaires %>%
  select(rank, person_name, final_worth, state) %>%
  filter(state!="NA") %>%
  arrange(-final_worth)
```

```{r}
billionaires %>%
  select(rank, person_name, final_worth, state) %>%
  filter(state!="NA") %>%
  arrange(-final_worth) %>%
  count(state) %>%
  arrange(-n) %>%
  head(15) %>%
  ggplot(aes(x=state, y=n)) + 
  geom_col(color = "brown", fill = "plum", alpha = 0.8)+
  theme_linedraw() + 
  theme(plot.title = element_text(size = 12, face = "bold"),
        axis.title = element_text(size=10),
        axis.text.x = element_text(size=7, angle = 65, hjust=1))+
  labs(title = "Distribution of the No. of Billionaires by State",
       x = "State",
       y = "No. of Billionaires")
```

Conclusion: Within the US, you can have a significantly higher net worth if you're in California, New York or Florida.
