---
title: "Analysis of Category (field to be in)"
output: html_document
date: "2023-03-13"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Arranging companies by profit and assigning categories to the top 20 companies, comparing the count of field for this to the count of billionaries' categories by final worth

Finding the specific categories for the billionaire dataset
```{r}
billionaires %>%
  count(category) %>% 
  arrange(-n)
```

Assigning categories to the top 20 most profitable companies
```{r}
companies_profit <- companies %>% 
  arrange(-profit_bil) %>% 
  select(rank, global_company, country, profit_bil, market_value_bil) %>% 
  mutate(category=case_when(
    global_company =="Saudi Arabian Oil Company (Saudi Aramco)" ~ "Energy",
    global_company =="Apple" ~ "Technology",
    global_company =="Berkshire Hathaway" ~ "Finance & Investments",
    global_company =="Alphabet" ~ "Technology",
    global_company =="Microsoft" ~ "Technology",
    global_company == "ICBC" ~ "Finance & Investments",
    global_company == "China Construction Bank" ~ "Finance & Investments",
    global_company == "JPMorgan Chase" ~ "Finance & Investments",
    global_company == "Meta Platforms" ~ "Technology",
    global_company == "Agricultural Bank of China" ~ "Finance & Investments",
    global_company == "Tencent Holdings" ~ "Technology",
    global_company == "Samsung Group" ~ "Technology",
    global_company == "Bank of China" ~ "Finance & Investments",
    global_company == "Amazon" ~ "Technology",
    global_company == "Bank of America" ~ "Finance & Investments",
    global_company == "Vivendi" ~ "Media & Entertainment",
    global_company == "Toyota Motor" ~ "Automotive",
    global_company == "Mercedes-Benz Group" ~ "Automotive",
    global_company == "Gazprom" ~ "Energy",
    global_company == "Novartis" ~ "Healthcare"
    ))
```

```{r}
companies_profit %>% 
  head(20) %>% 
  count(category) %>% 
  arrange(-n)
```

For the top 20 most profitable companies, it appears that Finance & Investments and Technology are the most abundant categories for these companies.

Billionaires categories by Final Worth
```{r}
billionaires %>% 
  select(rank, person_name, final_worth, category, country) %>% 
  arrange(-final_worth) %>% 
  head(20) %>% 
  count(category) %>% 
  arrange(-n)
```

However, based on billionaire final worth, it appears that the top 20 billionaires belong to the technology or fashion & retail sector.

Conclusion: Technology being the highest for both, would be the most popular field to enter to maximize your of becoming a billionaire, with Finance & investments and Fashion & retail being close seconds.