---
title: "Exploratory_age_analysis"
output: html_document
date: "2023-03-09"
---
```{r}
library(shiny)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Exploratory analysis of datasets

```{r}
glimpse(billionaires)
```

```{r}
summary(companies)
```

```{r}
billionaires %>%
  count(category) %>% 
  arrange(-n)
```

```{r}
filter(year!= "NA") %>% 
  select(rank, person_name, final_worth, category, age, year, month) %>% 
  count(year) %>% 
  arrange(-n) %>%
  ggplot(aes(x=year))
```

## Age parameter - how old should you be to be more profitable and maximise your chances of being a billionaire 
```{r}
billionaires_age <- billionaires %>% 
  arrange(-final_worth) %>% 
  separate(birth_date, into = c("month", "date", "year"), sep ="/")
billionaires_age
```
```{r}
billionaires_age$year = as.numeric(billionaires_age$year)
```

```{r}
billionaires_age
```

```{r}
billionaires_age %>%
  count(year) %>%
  arrange(-n) %>%
  filter(year!= "NA") %>%
  ggplot(aes(x=year, y=n)) + 
  geom_line(color="plum") + 
  theme_light() + 
  theme(plot.title = element_text(size = 12, face = "bold"),
        axis.title = element_text(size=8),
        axis.text.x = element_text(size=5.5, angle = 80, hjust=1))+
  labs(title = "Distribution of the No. of Billionaires by Year of Birth",
       x = "Year of Birth",
       y = "No. of Billionaires")
```

The best year to have been born to become a billionaire is 1963 with 83 billionaires being born that year.
If you are currently 55 and above, you have a great chance of becoming a billionaire

People having the most wealth are currently around 60 years of age (2023-1963). 
Therefore, if you follow the current proposed country + category, you will likely become a billionaire by the year 2062. (2002+60)

## Unused sections for the presentation but relevant exploratory work

# App that shows final worth of billionaires by the field they are in - not using
```{r}
billionaires%>% 
  select(person_name, final_worth, category) %>%
  arrange(-final_worth) %>%
  head(10)%>%
  ggplot(aes(x=person_name, y=final_worth, fill=category))+ 
  geom_col(alpha=0.4) + 
  facet_wrap(~category, ncol=2)+
  theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  labs(title = "Final Worth by Billionaire and Field",
       x = NULL,
       y = "Final Worth",
       fill = "Field")
```

# Mutate NPM to add field - not using
```{r}
companies_NPM_new <- companies_NPM %>%
  mutate(category=case_when(
    global_company =="Shenzhen Feima International Supply Chain Co., Ltd." ~ "Logistics",
    global_company =="Porsche Automobil Holding" ~ "Automotive",
    global_company =="Sofina" ~ "Finance & Investments",
    global_company =="PT Saratoga Investama Sedaya" ~ "Finance & Investments",
    global_company =="3i Group" ~ "Finance & Investments",
    global_company == "Info Edge India" ~ "Technology",
    global_company == "Kinnevik" ~ "Finance & Investments",
    global_company == "Segro" ~ "Real Estate",
    global_company == "Akelius Residential Property" ~ "Real Estate",
    global_company == "Power Assets Holdings" ~ "Energy"))
```

## Trying to find the companies with the best market value and profit margins - not using
```{r}
companies_1 <- companies %>% 
  mutate(mv_profit_bil = profit_bil/market_value_bil *100) %>% 
  filter(global_company != "Bradespar") %>% 
  arrange(-mv_profit_bil)
```
