---
title: "How to Become a Billionaire"
output: html_document
date: "2023-02-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library("tidyverse")

library("janitor")

library("naniar")
```


```{r}
getwd()
```

```{r}
billionaires<- read.csv("forbes_dataset_2022/forbes_billionaires_2022.csv", na="")
billionaires
```
```{r}
billionaires <- janitor::clean_names(billionaires)
```

```{r}
companies <- read.csv("forbes_dataset_2022/forbes_companies_2022.csv", na="")
companies
```
```{r}
companies <- janitor::clean_names(companies)
```


```{r}
glimpse(billionaires)
```
```{r
glimpse(companies)
```
```{r}
naniar::miss_var_summary(billionaires)
```
- "about" isn't important for analyzing data

- "state" NAs refer to people outside the US

- "title" may not have a current working position especially if they are not involved in an organization

- "philanthropyScore" interesting metric but a lot of data is not available - we might still be able to do something with this or find additional data.

- "organization" some wealth is from family, or several different organizations, we still have field they work in and source of wealth so hopefully that is okay 


```{r}
naniar::miss_var_summary(companies)
```
- checked through data, NAs are represented as "NA" and "" but switched all "" to "NA"



things we may want to analyze for: 

filter country to US - look at which states produce the most billionaires

what country has the most assests/profits?

histogram: frequency of people born over span of years 

connecting final worth of billionaires to the field they are in

something with final worth and if they are self made or not 