---
title: "how_to_become_a_billionaire_analysis"
output: html_document
date: "2023-03-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

------

```{r}
billionaires
```

```{r}
billionaires %>%
  count(category) %>% 
  arrange(-n)
```

## Age parameter - how old should you be to be more profitable and maximise your chances of being a billionaire
```{r}
billionaires %>% 
  arrange(-final_worth) %>% 
  separate(birth_date, into = c("month", "date", "year"), sep ="/") %>% 
  filter(year!= "NA") %>% 
  select(rank, person_name, final_worth, category, age, year, month) %>% 
  count(year) %>% 
  arrange(-n)
```


```{r}
billionaires %>% 
  arrange(-final_worth) %>% 
  separate(birth_date, into = c("month", "date", "year"), sep ="/") %>% 
  filter(year!= "NA") %>% 
  select(rank, person_name, final_worth, category, age, year, month) %>% 
  count(year)%>% 
  ggplot(aes(x=year, y=n))+
  geom_col()+
  theme(plot.title = element_text(size = 12, face = "bold"),
        axis.title = element_text(size=8),
        axis.text.x = element_text(size=5, angle = 80, hjust=1))+
  labs(title = "Distribution of the No. of Billionaires by Year of Birth",
       x = "Year of Birth",
       y = "No. of Billionaires")
```

The best year to have been born to become a billionaire is 1963 with 83 billionaires being born that year.
If you are currently 55 and above, you have a great chance of becoming a billionaire

People having the most wealth are currently around 60 years of age (2023-1963). 
Therefore, if you follow the current proposed country + category, you will likely become a billionaire by the year 2062. (2002+60)

## App that shows final worth of billionaires by the field they are in - not using

```{r}
companies
```

```{r}
billionaires%>% 
  select(person_name, final_worth, category) %>%
  arrange(-final_worth) %>%
  head(10)%>%
  ggplot(aes(x=person_name, y=final_worth, fill=category))+ 
  geom_col(alpha=0.4) + 
  facet_wrap(~category, ncol=2)+
  theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  labs(title = "Final Worth by Billionaire and Field",
       x = NULL,
       y = "Final Worth",
       fill = "Field")
```

## Mutate NPM to add field - not using

```{r}
companies_NPM_new <- companies_NPM %>%
  mutate(category=case_when(
    global_company =="Shenzhen Feima International Supply Chain Co., Ltd." ~ "Logistics",
    global_company =="Porsche Automobil Holding" ~ "Automotive",
    global_company =="Sofina" ~ "Finance & Investments",
    global_company =="PT Saratoga Investama Sedaya" ~ "Finance & Investments",
    global_company =="3i Group" ~ "Finance & Investments",
    global_company == "Info Edge India" ~ "Technology",
    global_company == "Kinnevik" ~ "Finance & Investments",
    global_company == "Segro" ~ "Real Estate",
    global_company == "Akelius Residential Property" ~ "Real Estate",
    global_company == "Power Assets Holdings" ~ "Energy"))
```

## Base plots for the app (NPM)
```{r}
companies_NPM %>%
  ggplot(aes(x=profit_bil, y=sales_bil)) + 
  geom_point()
```

```{r}
companies_NPM %>%
  count(country) %>%
  arrange(-n)
```

```{r}
#install.packages("shinydashboard")
library(shinydashboard)
```


```{r, eval=F, echo=T}
library(shinydashboard)
ui <- dashboardPage(
  dashboardHeader(title="NPM by Country"),
  dashboardSidebar(disable=T),
  dashboardBody(
fluidRow(
    box(
  selectInput("x", "Select Country", choices = c("United States", "Sweden", "Canada", "China", "Hong Kong", "United Kingdom", "Germany", "France", "Saudi Arabia", "Switzerland"), 
              selected = "United States"),
  sliderInput("pointsize", "Select the Point Size", min=.5, max=5, value=2.5, step=.5)
  ),
  
  box(
  plotOutput("plot", width="600px", height= "500px"))
)
)
)


server <- function(input, output, session) {
  session$onSessionEnded(stopApp)
  output$plot <- renderPlot({
    companies_NPM %>%
      filter(country==input$x) %>%
        ggplot(aes(x=profit_bil, y=sales_bil, color=country)) + 
  geom_point(size=input$pointsize) +
      theme_light() + 
      labs(
       x = "Profit (Billions)",
       y = "Sales (Billions)")
    
  })
  
}

shinyApp(ui, server)
```

## Mutating the profit/revenue column for net profit margin - is there a correlation between profit margins and market value?
```{r}
companies_NPM <- companies %>% 
  mutate(net_profit_margin_percent = profit_bil/sales_bil *100) %>% 
  filter(global_company != "Bradespar") %>% 
  arrange(-net_profit_margin_percent) %>%
  head(100)
companies_NPM
```

## Mutating the assets to sales ratio
```{r}
companies %>% 
  mutate(assets_sales_ratio = assets_bil/sales_bil) %>% 
  filter(global_company != "Bradespar") %>% 
  arrange(-assets_sales_ratio) %>% 
  head(10)
```

## Arrange by profit and see whether they also have highest market values - finish this and add the categories, see the count of field for this and compare to count of billionaries categories by final worth
```{r}
companies_profit <- companies %>% 
  arrange(-profit_bil) %>% 
  select(rank, global_company, country, profit_bil, market_value_bil) %>% 
  mutate(category=case_when(
    global_company =="Saudi Arabian Oil Company (Saudi Aramco)" ~ "Energy",
    global_company =="Apple" ~ "Technology",
    global_company =="Berkshire Hathaway" ~ "Finance & Investments",
    global_company =="Alphabet" ~ "Technology",
    global_company =="Microsoft" ~ "Technology",
    global_company == "ICBC" ~ "Finance & Investments",
    global_company == "China Construction Bank" ~ "Finance & Investments",
    global_company == "JPMorgan Chase" ~ "Finance & Investments",
    global_company == "Meta Platforms" ~ "Technology",
    global_company == "Agricultural Bank of China" ~ "Finance & Investments",
    global_company == "Tencent Holdings" ~ "Technology",
    global_company == "Samsung Group" ~ "Technology",
    global_company == "Bank of China" ~ "Finance & Investments",
    global_company == "Amazon" ~ "Technology",
    global_company == "Bank of America" ~ "Finance & Investments",
    global_company == "Vivendi" ~ "Media & Entertainment",
    global_company == "Toyota Motor" ~ "Automotive",
    global_company == "Mercedes-Benz Group" ~ "Automotive",
    global_company == "Gazprom" ~ "Energy",
    global_company == "Novartis" ~ "Healthcare"
    ))
```

```{r}
companies_profit %>% 
  head(20) %>% 
  count(category) %>% 
  arrange(-n)
```
For the top 10 most profitable companies, it appears that Finance & Investments and Technology are the most abundant categories for these companies.

Billionaire data

```{r}
billionaires %>% 
  select(rank, person_name, final_worth, category, country) %>% 
  arrange(-final_worth) %>% 
  head(20) %>% 
  count(category) %>% 
  arrange(-n)
```

However, based on billionaire final worth, it appears that the top 20 billionaires belong to the technology or fashion & retail sector.

Technology being the highest for both, would be the most popular field to enter to maximize your chances on the pathway to becoming a billionaire with Finance & investments and Fashion & retail being close seconds.

## Comparison of highest market value to lowest market value

Highest market value - top 10
```{r}
companies_MV_high <- companies %>% 
  arrange(-market_value_bil) %>% 
  head(10) %>% 
  select(global_company, country, market_value_bil) %>% 
  ggplot(aes(x=reorder(global_company, market_value_bil), y=market_value_bil, fill = country))+
  geom_col(color = "black")+
  coord_flip()+
  labs(title = " Highest Market Values of the Top 10 Global Companies by Country",
       x = "Market Value",
       y = "Global Company")
```

```{r}
companies_MV_high+
  theme_light()+
  theme(plot.title = element_text(size = 10, face = "bold"),
        axis.title = element_text(size=10),
        axis.text.x = element_text(size=9, hjust=1))
```

Lowest Market Value - Lower 10
```{r}
companies_MV_low <- companies %>% 
  arrange(market_value_bil) %>% 
  head(10) %>% 
  select(global_company, country, market_value_bil) %>% 
  ggplot(aes(x=reorder(global_company, market_value_bil), y=market_value_bil, fill = country))+
  geom_col(color = "black")+
  coord_flip()+
  labs(title = "Lowest Market Values of the Top 10 Global Companies by Country",
       x = "Market Value",
       y = "Global Company")
```

```{r}
companies_MV_low+
  theme_light()+
  theme(plot.title = element_text(size = 10, face = "bold"),
        axis.title = element_text(size=10),
        axis.text.x = element_text(size=9, hjust=1))
```

## Trying to find the companies with the best market value and profit margins - not using
```{r}
companies_1 <- companies %>% 
  mutate(mv_profit_bil = profit_bil/market_value_bil *100) %>% 
  filter(global_company != "Bradespar") %>% 
  arrange(-mv_profit_bil)
```

## Billionaire data
```{r}
billionaires_country <- billionaires %>% 
  count(country) %>% 
  arrange(-n) %>% 
  head(10) %>% 
  ggplot(aes(x=reorder(country,n), y=n))+
  geom_col(color = "black", fill ="coral1")+
  coord_flip()+
  labs(title = "No. of Billionaires by Country",
       x = "Country",
       y = "Number of Billionaires")
```

```{r}
billionaires_country+
  theme_light()+
  theme(plot.title = element_text(size = 10, face = "bold"),
        axis.title = element_text(size=10),
        axis.text.x = element_text(size=9, hjust=1))
```



## Companies by country Pie Chart
```{r}
companies %>% 
  count(country) %>% 
  arrange(-n) %>% 
  head(10) %>% 
  ggplot(aes(x=country, y=n, fill=country))+
  geom_col()+
  coord_polar()
```


```{r}
prop <- c(590, 297, 196, 65, 64, 58, 55, 54, 54, 52)
pie(prop)
```

```{r}
myPalette <- brewer.pal(9, "BuPu")
pie(prop, labels = c("US", "China", "Japan", "S.Korea", "UK", "Canada", "India", "France", "Hong Kong", "Germany"), border = "black", col=myPalette)
```

## arrange them by final worth and see which states have the highest (filter for na.rm = T so that only US states show up)

```{r}
billionaires
```
```{r}
billionaires %>%
  select(rank, person_name, final_worth, state) %>%
  filter(state!="NA") %>%
  arrange(-final_worth) %>%
  count(state) %>%
  arrange(-n)
```


```{r}
billionaires %>%
  select(rank, person_name, final_worth, state) %>%
  filter(state!="NA") %>%
  arrange(-final_worth)
```




